My title

### 2022-02-28 outputs/paper/paper.Rmd

LGBT is the acronym of the following 4 genders, **L** for Lesbian, **G** for gay, **B** for bisexual, **T** for transgender. By definition, these genders by definition should have a much lower birth rate than heterosexual. Thus, the population changes in these population are very likely to make an impact on the birth rate of the US.

@@

Figure \@ref(fig:fig-gender-raising-children-distribution) shows the gender distribution of LGBT and Same Sex Couple as well as the percentage raising children.
Figure \@ref(fig:fig-gender-raising-children-distribution) (a) and Figure \@ref(fig:fig-gender-raising-children-distribution) (c) clearly shows that more females are non-heterosexual.
This should make a even larger impact on birth rate as only females are able to give births (in normal situations).

Figure \@ref(fig:fig-gender-raising-children-distribution) (b) shows the percentage of LGBT population that raise children. 71% of the LGBT population don't raise children. With these information, we can conclude that the growth of LGBT population is able to cause a negative change in birth rate.

@@

[@cite_original]

@@

@@

```{r echo = FALSE, fig-LGBT-socioeconomic-indicators, fig.cap='LGBT Socioeconomic Indicators', fig.asp=1, fig.ncol = 1, out.width='.80\\linewidth', fig.align="center"}
knitr::include_graphics("./images/LGBT-socioeconomic-indicators.png")
```

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

>>>>

LGBT is the acronym of the following 4 genders, **L** for Lesbian, **G** for gay, **B** for bisexual, **T** for transgender. By definition, these genders by definition should have a much lower birth rate than heterosexual. Then change in birth rate and change in LGBT population should have a negative propotional relationship (i.e. Growth in LGBT population leads to lower birth rate).
Thus, the population changes in these population are very likely to make an impact on the birth rate of the US.

If we assume the simpliest case where we ignore race, gender distribution (equal percentage of male and female) and all other factors, and assume that no LGBT or same sex couple population give birth to a child, then there would be a perfect correlation (perfectly proportional) between LGBT population change and birth rate (i.e. a $x\%$ increase in LGBT population could lead to $x\%$ decrease in birth rate). Let's define $\phi = \frac{\Delta Birth Rate}{\Delta LGBTPopulation}$ and call $\phi$ the BirthRate-LGBT coefficient for convenience. If we take other factors into account, the impact to birth rate could be even larger (i.e. $\phi<-1$).

@@

Figure \@ref(fig:fig-gender-raising-children-distribution) shows the gender distribution of LGBT and Same Sex Couple as well as the percentage raising children.
Figure \@ref(fig:fig-gender-raising-children-distribution) (a) and Figure \@ref(fig:fig-gender-raising-children-distribution) (c) clearly shows that more females are non-heterosexual.
This should make a even larger impact ($\phi<-1$) on birth rate as only females are able to give births (in normal situations).

Figure \@ref(fig:fig-gender-raising-children-distribution) (b) shows the percentage of LGBT population that raise children. 71% of the LGBT population don't raise children.

@@

@@

From \@ref(fig:fig-race-distribution) we can see that White population takes up the majority of the population of LGBT and Same Sex Couple. White is also the majority of the population of the US. Thus, larger LGBT population could lead to a even larger decrease in birth rate ($\phi<-1$).

@@

From \@ref(fig:fig-age-distribution) (a) we can see that most same sex couples fall in the age group 25-64. This period overlaps with the majority of the childbearing age. From \@ref(fig:fig-age-distribution) (b), we can see that LGBT population decreases as age increases starting from the age or 18, which is the beginning of women's childbearing age. These 2 evidences also growth of LGBT population could lead to a larger decrease in birth rate ($\phi < -1$).

With these information, we can conclude that the growth of LGBT population is able to cause a negative change in birth rate.

```{r echo = FALSE, fig-LGBT-socioeconomic-indicators, fig.cap='Socioeconomic Indicators', fig.asp=1, fig.ncol = 1, out.width='.80\\linewidth', fig.align="center"}
knitr::include_graphics("./images/LGBT-socioeconomic-indicators.png")
```

Figure \@ref(fig:fig-LGBT-socioeconomic-indicators) shows some Socioeconomic Indicators classified by sexual orientation (LGBT or not), such as employment status, income level education level, and whether or not being insured and food insecure. Darker color represents LGBT, lighter color represents non-LGBT.
From the plots, we can extract some socioeconomic indicators of LGBT. Comparing to non-LGBT population, LGBT are more likely to be unemployed, uninsured, being food insecure, having a low income (lower then $24k), and having a lower education level (percentage of LGBT population with Bachelor's or post-grad degree is lower than that of the percentage of non-LGBT population).
